---
title: "Analysis of Hotel Booking in relation to child stay."
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, include=FALSE}
library(tidyverse)
library(dplyr)
library(tidytext)
library(GGally)
hotels <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-02-11/hotels.csv")
```

**This analysis contains hotel booking data from the Year 2015 - 2017. The data is processed to display the booking result in two different hotels with and without children.**

**We will analyse only the records where the guest stayed and remove removing unnecessary columns and cancelled booking data.**
```{r}
hotels <- hotels %>% select(hotel, is_canceled, arrival_date_month, stays_in_weekend_nights, stays_in_week_nights, adults, children, babies, meal, reserved_room_type, assigned_room_type, adr, required_car_parking_spaces, total_of_special_requests)

hotel_stayed <- hotels %>%
  filter(is_canceled == 0)

hotel_stayed <- hotel_stayed %>%
  select(-c("is_canceled"))

```

**Combining children and baby stay to one column and changing numeric to character. Same with parking space.**
```{r}
hotel_stayed<- hotel_stayed %>% mutate(children = case_when(
  children + babies >0 ~"children", TRUE ~ "none"),
  required_car_parking_spaces = case_when(
    required_car_parking_spaces > 0 ~ "parking", TRUE ~ "none"
  )
  ) %>% select(-babies)
```

**Converting arrival month to factor to rearrange from Jan - Dec.**
```{r}

hotel_stayed %>% 
  mutate(arrival_date_month = factor(arrival_date_month, levels = month.name)) %>% 
  count(hotel, arrival_date_month, children) %>%
  group_by(hotel, children) %>%
  mutate(proportion =  n/sum(n))
  
```

**Plot displaying 2 hotel, City and Resort Hotel, number of the guest with and without children throughout the year. The data from 3 years are combined according to the month and displayed in the graph below.**
```{r}
hotel_stayed %>% 
  mutate(arrival_date_month = factor(arrival_date_month, levels = month.name)) %>% 
  count(hotel, arrival_date_month, children) %>% group_by(hotel, children) %>% 
  mutate(proportion = n/sum(n)) %>% 
  ggplot(aes(arrival_date_month, proportion, fill = children)) + 
  geom_col(position = "dodge") +
  scale_y_continuous(labels = scales::percent_format()) + 
  facet_wrap(~hotel, nrow = 2)
```

**Creating a plot for car parking spaces required for hotel bookings. Displaying 2 hotel, City and Resort Hotel, guest requesting car park with children and without children.**
```{r}
hotel_stayed %>% count(hotel, required_car_parking_spaces, children) %>% 
  group_by(hotel, children) %>% mutate(proportion = n/sum(n)) %>% 
  ggplot(aes(required_car_parking_spaces, proportion, fill = children)) + geom_col(position = "dodge") +
  scale_y_continuous(labels = scales::percent_format()) + 
  facet_wrap(~hotel, nrow = 2)
```

