---
title: "Titanic Machine Learning for Disaster"
author: "Dinesh"
date: "29/06/2020"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(readr)
library(dplyr)
library(gridExtra)
library(tidyverse)
library(randomForest)
library(GGally)
test <- read_csv("~/Desktop/CSV/Kaggle/test.csv")
train <- read_csv("~/Desktop/CSV/Kaggle/train.csv")
```


**Two files were loaded, Test.csv and Train.csv. The column name for data contains uppercase, so renaming them with lowercase.**
```{r}
names(test) <- tolower(names(test))
names(train) <- tolower(names(train))
```

**Adding survived column missing in Test data and combining both of them in single dataframe, df_titanic.**
```{r}
test<- test %>% mutate(survived = "none")
train<- train[, c(1,3:12,2)]
head(test, 2)
head(train, 2)
df_titanic <- rbind(train, test)
```

**Plotting data according to Passenger Class and Survived according to sex.**
```{r}

ggplot(train, aes(x = pclass, fill = as.factor(survived))) + geom_bar() + labs(fill = "survived") +facet_wrap(~sex) + theme_bw()

```

**Name contains Mr, Mrs, Miss etc. Creating a new column according to title. If not specific then other.**
```{r}
df_titanic <- df_titanic %>% mutate(title = case_when(str_detect(name, "Mr.") ~ "Mr",
                                         str_detect(name, "Mrs.") ~ "Mrs",
                                         str_detect(name, "Miss.") ~ "Miss",
                                         str_detect(name, "Master.") ~ "Master",
                                         TRUE ~ "other"
                                         ))
```

**Title has Dr, Rv etc. so converting them into male according to sex.**
```{r}
for(i in 1:nrow(df_titanic)){
  if(df_titanic[i,13] == "other"){
    if(df_titanic[i,4] == "male"){df_titanic[i, 13] = "Mr"}
  }
}

df_titanic %>% count(fare, sort =  TRUE)
```

**The survival rate depends on the fare of the ticket. So, grouping people according to fare.**
Fare is 20 or less then, low.
Fare is more than 20 and less then or equalt to 50, low-medium.
Fare is more than 50 and less then or equalt to 75, medium.
Fare is75 or more, high.
```{r}
df_titanic <- df_titanic %>% mutate(fare_div = ifelse(fare <= 20, "low",
                                   ifelse(fare>20 & fare<=50, "low-medium",
                                          ifelse(fare>50 & fare<= 75, "medium", "high"))))
df_titanic %>% filter(survived %in% c(0,1)) %>% ggplot( aes(x = fare_div, fill = as.factor(survived))) + geom_bar() + labs(fill = "survived") +facet_wrap(~fare_div)
```

**Plotting according to newly generated data, title and displaying survived data.**
```{r}
df_titanic %>% filter(survived %in% c(0,1)) %>% ggplot( aes(x = pclass, fill = as.factor(survived))) + geom_bar() + labs(fill = "survived") +facet_wrap(~title) + theme_bw()
```

**Building a model for prediction according to combined ("pclass", "title","sex","fare_div").**
```{r}
rf_train1<- df_titanic[1:891, c("pclass", "title","sex","fare_div")]
rf_label <- as.factor(df_titanic[1:891,]$survived)
set.seed(1234)
rf1 <- randomForest(x = rf_train1, y = rf_label, importance = TRUE, ntree = 1000)
rf1

```

**Making prediction according t the prediction.**
```{r}
test_predict_df<- df_titanic[892:1309, c("pclass", "title","sex","fare_div")]
test_predict_df<- test_predict_df %>% replace_na(list(fare_div = "low"))
r1_predict<- predict(rf1, test_predict_df)
final_df <- data.frame(test_predict_df, survived = r1_predict)
final_df %>% count(survived, sort = TRUE)

```

**Plotting the output according to sex and fare division.**
```{r, warning= FALSE}

ggplot(data = final_df, aes(x = sex, fill = as.factor(survived)) ) + geom_bar() + theme_bw() + labs(fill = "survived") + facet_wrap(~fare_div)

final_df %>% ggpairs(mapping = aes(color = survived))


```


